Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-11-08 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-M code added

@@

@@

>>>>

```{r medicalSampleInfo}
# extract demographic information from eligibility questionnaire
medicalDemographicSupp <- 
  dtMedical$raw.eligibility %>%
  filter(session %in% dtMedical$full$session) %>%
  select(session, nationality, studentBachMa)
# summarize participant characteristics

medicalSampleInfo <-
  merge(dtMedical$full, medicalDemographicSupp, by = "session") %>%
  mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>%
  group_by(PID) %>%
  summarise(
    dailiesN = n(), 
    morningN = sum(periodMA=="morning"),
    afternoonN = sum(periodMA=="afternoon"),
    age = age,
    gender = gender,
    nationality = nationality
  ) %>%
  distinct

# look at frequencies of characteristics 
table(medicalSampleInfo$age)
table(medicalSampleInfo$gender)
table(as.character(medicalSampleInfo$nationality))
```

```{r medicalVarDescr}
medicalMlCor <-
  MlCorMat(
    data = dtMedical$full,
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
  )

medicalMlCor %>%
  kable(
    .,
    caption = "Medical: Multilevel Core Variable Descriptives",
    format = "html",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  )
```

```{r medicalOutVarDescr}
medicalOutMlCor <-
  MlCorMat(
    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
  )

medicalOutMlCor %>%
  kable(
    .,
    caption = "Medical: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "html",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  )

# misty::multilevel.descript(dtStudentsSupp$studentWithinBetween$keyMotiveFulfilled, cluster = dtStudentsSupp$studentWithinBetween$PID)
```

After receiving ethical approval from the University of Groningen, we recruited `r nrow(medicalSampleInfo)` international medical students using a contacts within the University Medical Department and specifically targeted non-Dutch students, who had recently arrived in the Netherlands. Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon). With this design, we aimed at getting 50-60 measurements per participant (*M* = `r format(round(mean(medicalSampleInfo$dailiesN),2), nsmall=2)`, *SD* = `r format(round(sd(medicalSampleInfo$dailiesN),2), nsmall=2)`, *total N* = `r sum(medicalSampleInfo$dailiesN)`). As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results. Participants were compensated for their participation with partial course credits --- depending on their participation. The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women). The sample fairly accurately describes the local population of international students.

The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, daily diary-, and post-measurement. The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (*median duration* = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, *MAD duration* = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).  General compliance was high (`r format(round(sum(medicalSampleInfo$dailiesN)/(nrow(medicalSampleInfo)*62)*100,2), nsmall=2)`% filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS). The response rates were approximately equal during mornings (*n* = `r sum(medicalSampleInfo$morningN)`) and afternoons (*n* = `r sum(medicalSampleInfo$afternoonN)`). All key variables in for this study were part of the short daily diary surveys. 
The measurement of intergroup contacts was identical to study two. The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`% of individual daily diary measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`% of all `r nrow(dtMedical$full)` daily diary responses).

```{r medicalFreqAttCor}
dtMedicalSupp$medicalContactFreq <-
  dtMedicalSupp$medicalContactFreq %>%
  mutate(
    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
  )

# correlation panel
pairs.panels.new(
  dtMedicalSupp$medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
    "Sum:\nNumber of Outgroup Contacts (NL)",
    "Mean:\nInteraction Quality",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)

# correlation panel with interaction sums winsorized
pairs.panels.new(
  dtMedicalSupp$medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
    "Mean:\nInteraction Quality",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)
```

@@

We tested the most general contact hypothesis in two steps. First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes. Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions). We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (*r* = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (*r* = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). This is to say that within our data, participants with more outgroup interactions did not have significantly more positive or negative outgroup attitudes. This is again consistent with the results we found in the first study but inconsitent with the significant relationship we find in the second study.

```{r medicalModelOlsAttFreqQual}
# create list to store Worker models
mdlMedical <- list()

# regression
mdlMedical$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)

summ(
  mdlMedical$lmAttFreqQualX,
  confint = TRUE,
  digits = 3
)

mdlMedical$lmAttFreqQualXEta <-
  effectsize::eta_squared(mdlMedical$lmAttFreqQualX, partial = TRUE)

interactions::interact_plot(
  mdlMedical$lmAttFreqQualX,
  pred = SumContactNL_c,
  modx = AvQuality_c,
  interval = TRUE,
  partial.residuals = TRUE
)

interactions::johnson_neyman(mdlMedical$lmAttFreqQualX,
                             pred = SumContactNL_c,
                             modx = AvQuality_c,
                             alpha = .05)
```

However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (*r* = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (*b* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, *t*(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, *p* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`). Given the missing aggregate relationship between number of interactions and outgroup attitudes, we find no significant effect of interactions themselves nor do we find a significant interaction effect. This result mirrors that of study one but is inconsistent with the second study. But again this inconsistency is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.

```{r medicalModelMLAttNull}
# Create and save Model
mdlMedical$lmerAttNullType <-
  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
             data = dtMedical$full %>%
               filter(complete.cases(
                 OutgroupInteraction, NonOutgroupInteraction
               ))) # use optim if it does not converge

mdlMedical$lmeAttNullType <-
  lme(
    AttitudesDutch ~ 1,
    random = ~ 1 | PID,
    data = dtMedical$full %>%
      filter(complete.cases(
        OutgroupInteraction, NonOutgroupInteraction
      )),
    na.action = na.omit,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

# Get summary with p-values (Satterthwaite's method)
# summary(mdlMedical$lmerAttNull) #or with the lme function
summ(mdlMedical$lmerAttNullType, digits = 3)

# Save variances
mdlMedical$varAttNullType <- 
  VarCorr(mdlMedical$lmeAttNullType) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedical$tauAttNullType <- 
  as.numeric(mdlMedical$varAttNullType[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedical$sigmaAttNullType <- 
  as.numeric(mdlMedical$varAttNullType[2])
# The ICC estimate (between/between+within) is:
mdlMedical$IccAttNullType <-
  (as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))
mdlMedical$IccPercAttNull <-
  ((as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))) * 100
```

```{r medicalModelInterceptAttType, include = FALSE}
# Create and save Model
mdlMedical$lmeInterceptAttType <-
  lme(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
    random =  ~ 1 | PID,
    na.action=na.omit,
    data = dtMedical$full
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedical$lmerInterceptAttType <- lmer(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
    data = dtMedical$full
  ),
  confint = TRUE,
  digits = 3
)

mdlMedical$lmerInterceptAttTypeCI <- 
  confint(method = "Wald", mdlMedical$lmerInterceptAttType)

# Compare new model to previous step
anova(mdlMedical$lmeAttNullType, 
      mdlMedical$lmeInterceptAttType) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  add_rownames(., var = "Description") %>%
  mutate(Description = gsub(".*\\$", "", Description)) %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "html",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlMedical$varInterceptAttType <- 
  lme4::VarCorr(mdlMedical$lmeInterceptAttType)
```

```{r medicalModelSlopesInteractionType}
# Create and save Model (optimizer needed to reach convergence)
mdlMedical$lmeSlopesAttType <- lme(
  AttitudesDutch ~
    OutgroupInteraction + NonOutgroupInteraction,
  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
  control = lmeControl(opt = "optim"),
  na.action = na.omit,
  data = dtMedical$full
)

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedical$lmerSlopesAttType <- lmer(
    AttitudesDutch ~
      OutgroupInteraction + NonOutgroupInteraction +
      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
    data = dtMedical$full
  ), 
  confint = TRUE,
  digits = 3
)

mdlMedical$lmerSlopesAttTypeCI <- 
  confint(method = "Wald", mdlMedical$lmerSlopesAttType)

# Compare new model to previous step
anova(mdlMedical$lmeAttNullType,
      mdlMedical$lmeInterceptAttType, 
      mdlMedical$lmeSlopesAttType) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  add_rownames(., var = "Description") %>%
  mutate(Description = gsub(".*\\$", "", Description)) %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "html",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlMedical$varSlopesAttType <- 
  lme4::VarCorr(mdlMedical$lmeSlopesAttType)

# Assumption Checks:
mdlMedical$diagSlopesAttType <-
  sjPlot::plot_model(mdlMedical$lmerSlopesAttType, type = "diag")
grid.arrange(
  mdlMedical$diagSlopesAttType[[1]],
  mdlMedical$diagSlopesAttType[[2]]$`PID`,
  mdlMedical$diagSlopesAttType[[3]],
  mdlMedical$diagSlopesAttType[[4]]
)

# Plot prediction model
mdlMedical$predSlopesAttType <-
  dtMedical$full %>%
  filter(complete.cases(OutgroupInteraction, NonOutgroupInteraction)) %>%
  select(AttitudesDutch, TIDnum, PID) %>%
  mutate(measure = predict(
    mdlMedical$lmeSlopesAttType,
    dtMedical$full %>%
      filter(complete.cases(
        OutgroupInteraction, NonOutgroupInteraction
      )),
    re.form = NA
  ))

(
  mdlMedical$predPltSlopesAttType <-
    ggplot(data = mdlMedical$predSlopesAttType %>% filter(PID %in% dtMedicalSupp$medicalPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/Medical_PredictionPlot_SlopesAttType.png",
  mdlMedical$predPltSlopesAttType,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently). Thus, in our third dataset we find some mixed results, outgroup contacts are not significantly related to outgroup attitudes on aggregate between participants and this effect is also not suppressed by a average interaction quality (i.e., no interaction effect). However, while the aggregate data is partly inconsistent with the first two studies, the within person contemoranous effect of intergroup contact is consistent across all three studies.

@@

```{r medicalOutModelMLAttNull}
# create empty list to organize models
mdlMedicalOut <- 
  list(
    Att = list(),
    Qlt = list()
  )

# Create and save Model
mdlMedicalOut$Att$lmerNull <-
  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
mdlMedicalOut$Att$lmeNull <-
  lme(
    AttitudesDutch ~ 1,
    random = ~ 1 | PID,
    data = dtMedicalSupp$medicalOutWithinBetween,
    na.action = na.omit,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

# Get summary with p-values (Satterthwaite's method)
# summary(Null.Out.ML.r) #or with the lme function
summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE)

# Save variances
mdlMedicalOut$Att$varNull <- 
  VarCorr(mdlMedicalOut$Att$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedicalOut$Att$tauNull <- 
  as.numeric(mdlMedicalOut$Att$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedicalOut$Att$sigmaNull <- 
  as.numeric(mdlMedicalOut$Att$varNull[2])
# The ICC estimate (between/between+within) is:
mdlMedicalOut$Att$IccNull <-
  (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))
mdlMedicalOut$Att$IccPercNull <-
  ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100
```

```{r medicalOutModelInterceptAttAllport}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllport <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Att$lmerInterceptAllport <-
    lmer(
      AttitudesDutch ~ AllportsCondition_cwc + (1 | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

mdlMedicalOut$Att$lmerInterceptAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllport)

# Compare new model to previous step
anova(mdlMedicalOut$Att$lmeNull, 
      mdlMedicalOut$Att$lmeInterceptAllport) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "html",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlMedicalOut$Att$varInterceptAllport <-
  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllport)
```

```{r medicalOutModelSlopesAttAllport}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesAllport <-
  lme(
    AttitudesDutch ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Att$lmerSlopesAllport <- lmer(
    AttitudesDutch ~
      AllportsCondition_cwc +
      (1 + AllportsCondition_cwc | PID),
    data = dtMedicalSupp$medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

# all variables standardized within PPT
summ(
  mdlMedicalOut$Att$lmerSlopesAllportZ <- lmer(
    AttitudesDutch_zwc ~
      AllportsCondition_zwc +
      (1 + AllportsCondition_zwc | PID),
    data = dtMedicalSupp$medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

# standardized coefficients
stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesAllport)

# 95%CIs
mdlMedicalOut$Att$lmerSlopesAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllport)

# Attempts at R^2
#r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesAllport)
performance::r2(mdlMedicalOut$Att$lmerSlopesAllport)
performance::model_performance(mdlMedicalOut$Att$lmerSlopesAllport)
performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
                                 mdlMedicalOut$Att$lmerInterceptAllport, 
                                 mdlMedicalOut$Att$lmerSlopesAllport)

# Compare new model to previous step
anova(mdlMedicalOut$Att$lmeNull, 
      mdlMedicalOut$Att$lmeInterceptAllport, 
      mdlMedicalOut$Att$lmeSlopesAllport) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Student: Model Comparison",
    format = "html",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlMedicalOut$Att$varSlopesAllport <- 
  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesAllport)

# Assumption Checks:
mdlMedicalOut$Att$diagSlopesAllport <- 
  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesAllport, type = "diag")
grid.arrange(
  mdlMedicalOut$Att$diagSlopesAllport[[1]],
  mdlMedicalOut$Att$diagSlopesAllport[[2]]$`PID`,
  mdlMedicalOut$Att$diagSlopesAllport[[3]],
  mdlMedicalOut$Att$diagSlopesAllport[[4]]
)

# Plot prediction model
mdlMedicalOut$Att$predSlopesAllport <- 
  dtMedicalSupp$medicalOutWithinBetween %>% 
  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllport,
                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
                           re.form = NA
                           )
         )

(
  mdlMedicalOut$Att$predPltSlopesAllport <-
    ggplot(data = mdlMedicalOut$Att$predSlopesAllport, 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap( ~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllport.png",
  mdlMedicalOut$Att$predPltSlopesAllport,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

```{r medicalOutModelMLQltNull}
# Create and save Model
mdlMedicalOut$Qlt$lmerNull <-
  lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
mdlMedicalOut$Qlt$lmeNull <-
  mdlMedicalOut$Qlt$lmeNull <-lme(
    qualityOverall ~ 1,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

# Get summary with p-values (Satterthwaite's method)
# summary(Null.Out.Qual.ML.r) #or with the lme function
summ(mdlMedicalOut$Qlt$lmerNull, digits = 3)

# Save variances
mdlMedicalOut$Qlt$varNull <- 
  VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances
# The estimate of (between-group or Intercept variance, tau_{00}^2):
mdlMedicalOut$Qlt$tauNull <- 
  as.numeric(mdlMedicalOut$Qlt$varNull[1])
# and the estimate of (within-group or residual variance, sigma^2) is:
mdlMedicalOut$Qlt$sigmaNull <- 
  as.numeric(mdlMedicalOut$Qlt$varNull[2])
# The ICC estimate (between/between+within) is:
mdlMedicalOut$Qlt$IccNull <-
  (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))
mdlMedicalOut$Qlt$IccPercNull <-
  ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100
```

```{r medicalOutModelInterceptQltAllport}
# Create and save Model
mdlMedicalOut$Qlt$lmeInterceptAllport <-
  lme(
    qualityOverall ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Qlt$lmerInterceptAllport <-
    lmer(
      qualityOverall ~ AllportsCondition_cwc + (1 | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

mdlMedicalOut$Qlt$lmerInterceptAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptAllport)

# Compare new model to previous step
anova(mdlMedicalOut$Qlt$lmeNull, 
      mdlMedicalOut$Qlt$lmeInterceptAllport) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Medical: Model Comparison",
    format = "html",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlMedicalOut$Qlt$varInterceptAllport <-
  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptAllport)
```

```{r medicalOutModelSlopesQltAllport}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Qlt$lmeSlopesAllport <-
  lme(
    qualityOverall ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Qlt$lmerSlopesAllport <-
    lmer(
      qualityOverall ~
        AllportsCondition_cwc +
        (1 + AllportsCondition_cwc | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

mdlMedicalOut$Qlt$lmerSlopesAllportCI <- 
  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesAllport)

# Compare new model to previous step
anova(mdlMedicalOut$Qlt$lmeNull, 
      mdlMedicalOut$Qlt$lmeInterceptAllport, 
      mdlMedicalOut$Qlt$lmeSlopesAllport) %>%
  as.data.frame() %>%
  select(-call) %>%
  mutate(
    L.Ratio = round(L.Ratio, 3),
    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
  ) %>%
  replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Medical: Model Comparison",
    format = "html",
    linesep = "",
    booktabs = T,
    align = rep("c", ncol(.)),
    digits = 3
  ) %>%
  kable_styling(position = "left")

# Save variances
mdlMedicalOut$Qlt$varSlopesAllport <- 
  lme4::VarCorr(mdlMedicalOut$Qlt$lmeSlopesAllport)

# Assumption Checks:
mdlMedicalOut$Qlt$diagSlopesAllport <-
  sjPlot::plot_model(mdlMedicalOut$Qlt$lmerSlopesAllport, type = "diag")
grid.arrange(
  mdlMedicalOut$Qlt$diagSlopesAllport[[1]],
  mdlMedicalOut$Qlt$diagSlopesAllport[[2]]$`PID`,
  mdlMedicalOut$Qlt$diagSlopesAllport[[3]],
  mdlMedicalOut$Qlt$diagSlopesAllport[[4]]
)

# Plot prediction model
mdlMedicalOut$Qlt$predSlopesAllport <- 
  dtMedicalSupp$medicalOutWithinBetween %>%
  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesAllport,
                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
                           re.form = NA
                           )
         )

(
  mdlMedicalOut$Qlt$predPltSlopesAllport <-
    ggplot(data = mdlMedicalOut$Qlt$predSlopesAllport %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesAllport.png",
  mdlMedicalOut$Qlt$predPltSlopesAllport,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

```

```{r medicalOutModelInterceptAttAllportQlt}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllportQlt <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Att$lmerInterceptAllportQlt <-
    lmer(
      AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc + (1 | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3
)

mdlMedicalOut$Att$lmerInterceptAllportQltCI <- 
  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllportQlt)
